---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

```
# calcWCD v.1.0.2

calcWCD calculates weighted copublication distance between a gene/protein and a disease/term in PubMed literature.

## Installation

The released version of calcWCD can be installed from this repo directly:

``` r
devtools::install_github("ed-lau/calcWCD")
```

## Updates

2023-07-15 v.1.0.1
Due to 2023 changes to the NCBI EUtils API limiting PubMed retrieval to 9999 items, calcWCD now uses the EuropePMC API to retrieve PMIDs.
A new `max_retrieval` argument is added to `pmid()` to limit the number of retrievals. 

## Example

A basic example using test PMID and Annotation data included in the package: 
```{r example, warning=F, message=F}
require(calcWCD)
w <- wcd(pmids = test_pmids, annot = test_annotation)

w

```

Distribution of WCD values in the test files:

```{r pressure, echo=FALSE, warning=F, message=F}

hist(w$WCD, main="Distribution of WCD values.")

```

## Reference
Edward Lau, Vidya Venkatraman, Cody T Thomas, Jennifer E Van Eyk, Maggie P. Y. Lam. Identifying high-priority proteins across the human diseasome using semantic similarity. bioRxiv 309203; doi: https://doi.org/10.1101/309203
